%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Cover Letter - Oda, Senior Data Analyst
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{0pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     TITLE NAME
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{}{\Huge{Ashbin Jaison}}{  \href{mailto:ashbinjaison@gmail.com}{ashbinjaison@gmail.com} | +47 486 251 21 |  \urlstyle{same}\href{https://www.linkedin.com/in/ashbin-jaison/}{LinkedIn}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     MAIN COVER LETTER CONTENT
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\currentdate{\today}
\lettercontent{Dear Selina Rummel,}

\lettercontent{I am applying for the Senior Data Analyst position in Oda's Shop Team. My background is in applied statistics and quantitative data science, and the core responsibilities of this role -- defining success metrics, analysing ambiguous problems with stakeholder input, and identifying flawed analytical assumptions -- are work I have done across two research and industry contexts.}

\lettercontent{What draws me to the Shop Team is Oda's investment in rigorous experimentation: over 100 trustworthy A/B tests completed in 2023 using a Bayesian framework, and a data-as-a-product philosophy that treats analytical outputs as first-class deliverables with quality standards. I want to work where analytical rigour directly shapes customer-facing decisions, not just informs them.}

\lettercontent{The skills that map most directly:}

{\raggedright\fontspec[Path = OpenFonts/fonts/raleway/]{Raleway-Medium}\fontsize{11pt}{13pt}\selectfont
\begin{itemize}
    \item \textbf{Impact metrics \& evaluation:} Defined success metrics and statistical evaluation frameworks across a 4-year programme; improved output quality by $\sim$40\% by systematically identifying and correcting flawed model assumptions.
    \item \textbf{Ambiguous problems with stakeholder input:} Gathered domain expert input to frame ambiguous analytical problems and deliver coherent findings; produced risk assessments and recommendations for insurance and maritime clients.
    \item \textbf{Python \& SQL analytics:} Core stack is Python (pandas, NumPy, scikit-learn, XGBoost) and SQL for data modelling and extraction; built and iterated on statistical models and evaluation pipelines in fast-moving project contexts.
    \item \textbf{AI-integrated workflows:} Use Claude Code actively as an analytical and development tool; comfortable working in AI-assisted, iterative environments where tooling evolves alongside the work.
\end{itemize}\par}
\vspace{6pt}

\lettercontent{I am available from early August. This is a fixed-term contract; I am well-suited to delivering impact quickly in that structure and would welcome the chance to discuss how my background fits the Shop Team's priorities.}

\begin{flushright}
\closing{Kind regards,\\}

\signature{Ashbin Jaison}
\end{flushright}
\end{document}
